Um \textit{Framework} de Desenvolvimento de Aplicações Ubíquas em Ambientes Inteligentes

### 2012-12-09 trunk/ labtempo-ubicomp-projects/UbicompMiddleware/doc/sbrc-2013-dm/ubicomp-middleware.tex
primeira correção da tradução

%%%%%%%%%%%%%%
%  RESUMOS   %
%%%%%%%%%%%%%%
\begin{abstract}
With recent advances in mobile computing and wireless communication technologies, we can see the emergence of a favorable construction of ubiquitous applications. This paper proposes a new framework for building such applications, providing a conceptual and implementation tools. We propose abstractions that allow developers to handle the resources distributed in the environment and interpret the context informationin in a simple and homogeneous way. In order to demonstrate the feasibility of the proposal, the concepts were implemented in a platform called SmartAndroid. This platform also includes an prototyping interface for ubiquitous applications, where settings can be tested before the acquisition of all devices, and interface composition of contextual rules, where end users can set preferences on the environment.
\end{abstract}

>>>>

%%%%%%%%%%%%%%
%  RESUMOS   %
%%%%%%%%%%%%%%
\begin{abstract}
With recent advances in mobile computing and wireless communication technologies, we can see the emergence of a favorable scenario for building ubiquitous applications. This work proposes a new framework that aims the building of those applications, providing a conceptual and implementation tools. We propose abstractions that allow developers to handle the resources spread in the environment in a simple and homogeneous way, and to interpret context informations. In order to demonstrate the feasibility of the proposal, the concepts were implemented in a platform named \textit{SmartAndroid}. An ubiquitous applications prototyping interface was implemented over this platform to allow the testing of different environment configurations before the acquisition of all devices; and also a context rules composition interface, where end users can define their preferences in the environment.
\end{abstract}
